---
title: "R case study1"
author: "shashvindu jha"
date: "28/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(rmarkdown)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyr)
library(data.table)
```

#case study questions
# 1.	Merge the datasets Customers, Product Hierarchy and Transactions as Customer_Final.
# Ensure to keep all customers who have done transactions with us and 
# select the join type accordingly.
# a.	Use the base merge()

```{r}
Customer= read.csv("D:\\download\\1.3 - R Case Studies (All 3 case studies for Foundation R)\\R case study 1 (Retail)\\Customer.csv",stringsAsFactors =F)
Transactions= read.csv("D:\\download\\1.3 - R Case Studies (All 3 case studies for Foundation R)\\R case study 1 (Retail)\\Transactions.csv",stringsAsFactors = F)
prod_cat_info= read.csv("D:\\download\\1.3 - R Case Studies (All 3 case studies for Foundation R)\\R case study 1 (Retail)\\prod_cat_info.csv",stringsAsFactors = F)
Customer$DOB=as.Date(Customer$DOB,format="%d-%m-%Y")
Transactions$tran_date=as.Date(Transactions$tran_date,format="%d-%m-%Y")
Cust_Tran=merge(x=Customer,y=Transactions, 
                by.x = "customer_Id",
                by.y = "cust_id",all.x = T)

Customer_Final=merge(x=Cust_Tran,y=prod_cat_info,
                     by.x=c( "prod_cat_code","prod_subcat_code"),
                     by.y = c("prod_cat_code","prod_sub_cat_code"),all.x=T)
summary(Customer_Final)
```



#b.by dplyr

```{r}
Cust_tarn=left_join(Customer,Transactions,by=c("customer_Id"="cust_id"))
Customer_Final=left_join(Cust_tarn,prod_cat_info,by=c("prod_cat_code","prod_subcat_code"="prod_sub_cat_code"),)
summary(Customer_Final)
```




```{r}
length(is.na(Customer_Final$customer_Id))
```
# 2.	Prepare a summary report for the merged data set.
# a.	Get the column names and their corresponding data types

```{r}
str(Customer_Final)
```
# b.Top/Bottom 10 observations
```{r}
head(Customer_Final,10)
tail(Customer_Final,10)
```
# c."Five-number summary" for continuous variables (min, Q1, median, Q3 and max)
```{r}

min(Customer_Final$total_amt,na.rm = T)
quantile(Customer_Final$total_amt,0.25,na.rm = T)
median(Customer_Final$total_amt,na.rm = T)
quantile(Customer_Final$total_amt,0.75,na.rm = T)
max(Customer_Final$total_amt,na.rm = T)
names(Customer_Final)
```
# d.Frequency tables for all the categorical variables
```{r}

Customer_Final %>% count(city_code,Gender,prod_cat,prod_subcat)

fre_gen=Customer_Final %>% count(Gender)
fre_gen
```
# 3.	Generate histograms for all continuous variables 
# and frequency bars for categorical variables
```{r}
hist(Customer_Final$Qty,xlab = "Weight",col = "yellow",border = "blue")
hist(Customer_Final$total_amt,xlab = "Weight",col = "red",border = "blue")
```
# 4.	Calculate the following information using the merged dataset :
#   a.	Time period of the available transaction data
```{r}
min_date= min(Customer_Final$tran_date,na.rm = T)
max_date= max(Customer_Final$tran_date,na.rm = T)
(Time_period=max_date-min_date)
```
# b.	Count of transactions where the total amount of transaction was negative
```{r}
a=Customer_Final$total_amt[Customer_Final$total_amt<0]
length(a)
```
# 5.	Analyze which product categories are more popular among females vs male customers.

```{r}
more_popular=Customer_Final %>% count(Gender,prod_cat)
more_popular
```
# 6.Which City code has the maximum customers
# and what was the percentage of customers from that city?
```{r}
max_cust=Customer_Final %>% count(city_code)
order_count=order(max_cust$n,decreasing = T)
city_count=max_cust[order_count,]
head(city_count,1)
total_cust=sum(max_cust$n)
(cust_per=(max(max_cust$n)/total_cust)*100)
```
#7.	Which store type sells the maximum products by value and by quantity?
```{r}
gp1=group_by(Customer_Final,Store_type)
x=summarise(gp1,total_qty=sum(Qty))
head(x,1)
```
# 8.	What was the total amount earned from the "Electronics" and "Clothing" categories from Flagship Stores?
```{r}
gp2=group_by(Customer_Final,Store_type)
s1=select(Customer_Final,Store_type,prod_cat,total_amt)
Flagship = s1[(s1$Store_type == "Flagship store") & (s1$prod_cat==c("Clothing","Electronics")),]
gp2=group_by(Flagship,prod_cat)
(x=summarise(gp2,total_amt=sum(total_amt)))
#-------------------------------------------------------------------------------------------------
filter1=filter(Customer_Final,Store_type == "Flagship store",prod_cat==c("Clothing","Electronics"))
gpf1=group_by(filter1,prod_cat)
summarise(gpf1,total_amt=sum(total_amt))
```
#   9.	What was the total amount earned from "Male" customers under the "Electronics" category?
```{r}
names(Customer_Final)
(s_male=select(Customer_Final,Gender,prod_cat,total_amt))
(male_elec=s_male[(s_male$Gender=="M")&(s_male$prod_cat=="Electronics"),])
(filter_m=filter(Customer_Final,Gender=="M",prod_cat=="Electronics"))
summarise(filter_m,total_sum=sum(total_amt))
```
#   10.	How many customers have more than 10 unique transactions, after 
#removing all transactions which have any negative amounts?

```{r}

positive_totamt <- dplyr::filter(Customer_Final,total_amt >= 0)
q10.ex <- positive_totamt%>%group_by(transaction_id,customer_Id)%>%dplyr::summarise(Frequency = n())
q10 <- dplyr::filter(q10.ex,Frequency > 10)
q10
```
#   11.	For all customers aged between 25 - 35, find out:
#   a.	What was the total amount spent for "Electronics" and "Books" product categories?
```{r}

x_1=Customer_Final
add_age=mutate(x_1,age=time_length(difftime(as.Date(Customer_Final$tran_date,format = "%Y-%m-%d"), 
                                            as.Date(Customer_Final$DOB,format = "%Y-%m-%d")), "years"))
agefilter=filter(add_age,between(age, 25, 35),prod_cat==c("Books","Electronics"))
agefilter=group_by(agefilter,prod_cat)
summarise(agefilter,total_sum=sum(total_amt))

```
#   b.	What was the total amount spent by these customers between 1st Jan, 2014 to 1st Mar, 2014?
```{r}

time_bwt =filter(add_age,between(age, 25, 35),between(tran_date, "2014-01-01", "2014-03-01"))
summarise(time_bwt,total_sum=sum(total_amt))
```
```{r}
age=time_length(difftime(as.Date(Customer_Final$tran_date,format = "%Y-%m-%d"), 
                     as.Date(Customer_Final$DOB,format = "%Y-%m-%d")), "years")
time_length(difftime(as.Date("2003-04-05"), as.Date("2001-01-01")), "years")


x_1=Customer_Final

(add_age=mutate(x_1,age=time_length(difftime(as.Date(Customer_Final$tran_date,format = "%Y-%m-%d"), 
                                    as.Date(Customer_Final$DOB,format = "%Y-%m-%d")), "years")))

```
```{r}
```
```{r}
```
